### 2018-10-03 sections/strategy_Htautau.tex
porting language editor comments

The analysis strategy adopted by the $\Htautau$ search follows closely that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.

@@

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared to $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (events with exactly three jets or at least four jets).
%This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
%The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
The event reconstruction is based on the strategy previously used in Ref.~\cite{Chen:2015nta}.

Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
As in Ref.~\cite{Chen:2015nta}, this compatibility is assessed via a likelihood function that depens on the reconstructed mass of the three-jet 
system and the two non-$b$-tagged jets.
For the remaining events, the selected jets are assigned to the different top quark decay products via a criterion based on 
minimising a sum of angular distances between objects. Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
are estimated by minimising a $\chi^2$ function based on the probability density functions for the angular distance of the visible and invisible
decay products in the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
measured $\met$. After the $\chi^2$ minimisation, an improved resolution is obtained on the determination of the Higgs boson four-momentum, and hence
its invariant mass, as well as on the four-momentum of the parent top quark. Following the event kinematic reconstruction, several kinematic variables
that discriminate between signal and background are defined. These variables are used in the multivariate analysis discussed in the next section.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{ccccc}
\toprule\toprule 
& \multicolumn{2}{c}{$\lephad$} & \multicolumn{2}{c}{$\hadhad$} \\
Variable & 3j & $\geq$4j & 3j & $\geq$4j  \\
\midrule
$m_{\tau\tau}^{\text{fit}}$                      	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{Hq}$                                	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
$p_{\text{T,1}}$                             	& $\times$  & $\times$ & $\times$  & $\times$ \\
$p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$\met$ $\phi$ centrality                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\parallel}^{\text{miss}}$          	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\perp}^{\text{miss}}$          	& $\times$  & $\times$  &             & \\
$m_{b j_1}$                   		        & $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{lep}j}$      			        & $\times$  & $\times$  &   	  & \\
$m_{\tau j}$      			        & $\times$  & $\times$  &   	  & \\
$x_1^{\text{fit}}$				& $\times$  &	$\times$  & $\times$  & $\times$ \\
$x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ \hline
\bottomrule\bottomrule
\end{tabular}
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
The description of each variable is provided in the text.}}
\label{tab:mva_var}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions), 
elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.

@@

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible tau decay products in the transverse plane. The transverse plane is transformed such that the direction of the tau decay products are 
orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$- and $y$-components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

Among these variables, the most discriminating ones are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$. A comparison between data and background prediction for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
A good description of the data by the background model is observed in all cases.
The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:BDT}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl4j/canv_.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
\caption{$\Htautau$ search: Comparison of the shape of the BDT discriminant distribution after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
and the total background (black solid) in the different search regions considered:
(a) ($\lephad$, 3j), (b) ($\lephad$, $\geq$4j), (c) ($\hadhad$, 3j), and (d) ($\hadhad$, $\geq$4j). }
\label{fig:BDT}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The analysis strategy adopted in the $\Htautau$ search follows closely that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.

@@

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared to $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (events with exactly three jets or at least four jets).
%This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
%The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
The event reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}.

Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
This compatibility is assessed via a likelihood function that depens on the reconstructed mass of the three-jet 
system and the two non-$b$-tagged jets.
For the remaining events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
minimising a sum of angular distances between objects. Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
are estimated by minimising a $\chi^2$ function based on the probability density functions for the angular distance of the visible and invisible
decay products in the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
measured $\met$. After the $\chi^2$ minimisation, an improved resolution is obtained on the determination of the Higgs boson four-momentum, and hence
its invariant mass, as well as on the four-momentum of the parent top quark. Following the event kinematic reconstruction, several kinematic variables
that discriminate between signal and background are defined. These variables are used in the multivariate analysis discussed in the next section.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{ccccc}
\toprule\toprule 
& \multicolumn{2}{c}{$\lephad$} & \multicolumn{2}{c}{$\hadhad$} \\
Variable & 3j & $\geq$4j & 3j & $\geq$4j  \\
\midrule
$m_{\tau\tau}^{\text{fit}}$                      	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{Hq}$                                	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
$p_{\text{T,1}}$                             	& $\times$  & $\times$ & $\times$  & $\times$ \\
$p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$\met$ $\phi$ centrality                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\parallel}^{\text{miss}}$          	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\perp}^{\text{miss}}$          	& $\times$  & $\times$  &             & \\
$m_{b j_1}$                   		        & $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{lep}j}$      			        & $\times$  & $\times$  &   	  & \\
$m_{\tau j}$      			        & $\times$  & $\times$  &   	  & \\
$x_1^{\text{fit}}$				& $\times$  &	$\times$  & $\times$  & $\times$ \\
$x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ 
%\hline
\bottomrule\bottomrule
\end{tabular}
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
The description of each variable is provided in the text.}}
\label{tab:mva_var}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

Boosted decision trees~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions), 
elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.

@@

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible $\tau$-lepton decay products in the transverse plane. The transverse plane is transformed such that the direction of the $\tau$-lepton decay products are 
orthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

Among these variables, the most discriminating are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$. A comparison between data and background prediction for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
A good description of the data by the background model is observed in all cases.
The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:BDT}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added to the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added to the background prediction.
The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl4j/canv_.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
\caption{$\Htautau$ search: Comparison of the distribution of the BDT discriminant after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
and the total background (black solid) in the different search regions considered:
(a) ($\lephad$, 3j), (b) ($\lephad$, $\geq$4j), (c) ($\hadhad$, 3j), and (d) ($\hadhad$, $\geq$4j). }
\label{fig:BDT}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
